Towards Detecting Stalkerware Through Network Traces

### 2019-03-19 paper/main.tex
Images of desktop lookalikes

The other category for stalkerware encompasses a large range of quality. Many 
apps advertised as stalkerware have absolutely no functionality other than 
advertisement of other apps. The few that are functional are often simplistic 
in both features and network patterns. Unlike the overt apps, however, the vast 
majority are usually free with advertisements. These apps can be easily 
identified and found with a few keywords such as "spy","track", "locate", or 
"find".

@@

\section{Methodology}
\subsection{Finding Apps}
We selected thirty apps from a list provided by the team of Cornell researchers 
who performed the original large scale study of 
stalkerware\cite{chatterjee_spyware_2018}. An 
additional fifteen apps were included as they were recently added to the app 
store. Apps were chosen for their diversity of purpose and the probability that 
they can be used as stalkerware. These apps are the most likely to be 
downloaded when a abuser without deep technical knowledge tries to install 
stalkerware since they are either the first result upon searching for 
stalkerware, or are well known spyware apps due to advertisement or other 
reasons.

>>>>

The other category for stalkerware encompasses a large range of quality. Many 
apps advertised as stalkerware have absolutely no functionality other than 
advertisement of other apps. The few that are functional are often simplistic 
in both features and network patterns. Unlike the overt apps, however, the vast 
majority are usually free with advertisements.

@@

\section{Methodology}
\subsection{Finding Apps}
We selected thirty apps from a list provided by the team of Cornell researchers 
who performed the original large scale study of 
stalkerware\cite{chatterjee_spyware_2018}. An 
additional fifteen apps were included as they were recently added to the Google 
Play store. We found these apps by searching for keywords such as 
"spy","track", "locate", or "find". Encouragingly, IPV-related search terms 
such as "track girlfriend" return no results on the Play store. On the other 
hand, that did not mean stalking apps were not available on the play store, it 
just meant that different search terms had to be used to find them. Apps were 
chosen for their diversity of purpose and the probability that 
they can be used as stalkerware. These apps are the most likely to be 
downloaded when an abuser without deep technical knowledge tries to install 
stalkerware since they are either the first result upon searching for 
stalkerware, or are well known spyware apps due to advertisements.
